% FEEDBACK
% Beta version is negatief - vervang door Trial version 
% "cross compiling" met streepje -> "cross-compiling"
% AT3 uitleggen -> Android Tor Tribler Tunneling
% Requirement is hardware accelerated encoding/decoding library -> gmpy?
% Niet hoeven wachten op ARMv8 of future development, maar het gebruik van geoptimaliseerde libraries

% Currently not viable -> Het is wel viable maar we hebben meer tijd nodig (bijv. voor gmp) 
% Diffie helman precision is noodzakelijk en daarvoor geoptimaliseerd, niet een general purpose large number.
\begin{abstract}
	\addcontentsline{toc}{chapter}{Abstract}
	Tribler is a decentralized peer-to-peer file sharing system. Recently the Tribler development team has introduced anonymous internet communication using a Tor-like protocol in their trial version. The goal of our bachelor project is to port their technology to Android devices. This is a challenging task because cross-compiling the necessary libraries such as libtorrent to the ARM CPU architecture is uncharted territory. We have successfully ported all dependencies of Tribler to Android. An application called AT3 has been developed that tests whether these libraries work. This application downloads a test torrent and measures critical information such as CPU usage and download speed. Based on this information we have concluded that it is currently not viable to run the anonymous tunnels on a smartphone. Running several layers of encryption is very computationally expensive and modern smartphones can not keep up. With future developments such as the ARMv8 architecture which support hardware AES encryption, running the anonymous tunnels might become possible.
\end{abstract}
