\section{The Global Square}
	\label{scc:tgs}
	Over the past years, Tribler had many contributors. One of these contributors is The Global Square (TGS). This organization has Github commits on the Dispersy and libswift project. They also worked on the Python for Android library and made steps to compile the libraries used by Tribler in Python for Android. Nowadays TGS has become inactive and are no longer contributing. In this section, we will first describe what TGS is and where they stand for. After that, we describe their contributions to Tribler.

	\subsection{What is The Global Square?}
		Roarmag, an online journal writing about the global struggle for real democracy, published a proposal in 2011 describing The Global Square: an online platform for our movement \cite{theglobalsquare}. Their proposal is to make an online platform where people of all nations can come together as equals to participate in the coordination of collective actions and the formulation of common goals and aspirations: The Global Square. This online platform could provide the following tools:
		\begin{itemize}
			\item An interactive map that lists all ongoing assemblies around the world.
			\item A search option to find squares, events etc.
			\item Individual pages for each local square/assembly where they can organize events and share information.
			\item A public and private messaging system so individual users and groups can communicate with each other.
		\end{itemize}
		Traditional social media such as Facebook and Twitter, only allow to share and promote content. TGS encourage the active participation of citizens and the consolidation of working groups in a local and global context between individuals and assemblies. TGS should be multilingual and open source so everyone can be part of the platform.
	
	\subsection{Their contribution to Tribler}
		TGS has their own Github repository where they host contributions to various projects \cite{theglobalsquaregithub}. Notable are the contributions to the libswift and dispersy projects. The last commits to these projects are over a year ago.
		
		Another important contribution has been done to the Python for Android project. TGS has added the libswift, netifaces and m2crypto libraries to the Python for Android project, making it possible to create an Android application bundle with these libraries included. This is an important contribution because it can be used as a first step to implement the Tribler community or anonymous tunnels on an Android device: Tribler is using some of these libraries.
		
	\subsection{Our project}
		We have discussed Tor, Tribler and have explained some libraries that Tribler is using and Python for Android. In this section, we will give an overview of our activities for the upcoming weeks.
		
		The idea is to port the experimental code of pull request 525 to the Android device. This experimental code is written in Python so we have two options: either write the code of the anonymous tunnels in Java or use the Python for Android library to run the Python code on an Android device. We think the second options is the most easy. The Global Square already worked on porting some libraries to the Android so we can extend on their work. There are some other libraries we have to port such as libtorrent and Dispersy. Overall, this project will not be easy but if we succeed, it could be a big step towards anonymous streaming on the Android device.

